---
title: Lecture 1
subtitle: Syllabus and Course Outline
format:
  clean-revealjs:
    self-contained: false
    chalkboard: true
    incremental: true
    code-annotations: hover
    scrollable: false

    # logo: logo-title-slide.png
author:
  - name: Byeong-Hak Choe
    email: bchoe@geneseo.edu
    affiliations: SUNY Geneseo
date: 2025-08-25
execute: 
  eval: true
  echo: true
callout-icon: false

from: markdown+emoji
include-after-body: target-hover.html # effect.html

# bibliography: refs.bib
---


```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)


theme_set(theme_fivethirtyeight()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.5),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.5),
                               margin = margin(0,10,0,0)),
                axis.text.x = element_text(size = rel(1.5)),
                axis.text.y = element_text(size = rel(1.5)),
                strip.text = element_text(size = rel(1.5)),
                legend.position = "top",
                legend.text = element_text(size = rel(1.5)),
                legend.title = element_text(size = rel(1.5))
                )
          )
```


# Instructor {background-color="#1c4982"}

## Instructor
### Current Appointment & Education

- Name: Byeong-Hak Choe.
- Assistant Professor of Data Analytics and Economics, School of Business at SUNY Geneseo.

- Ph.D. in Economics from University of Wyoming.
- M.S. in Economics from Arizona State University.
- M.A. in Economics from SUNY Stony Brook.
- B.A. in Economics & B.S. in Applied Mathematics from Hanyang University at Ansan, South Korea.
  - Minor in Business Administration.
  - Concentration in Finance.
  


## Instructor
### Economics and Data Science

- Choe, B.H., 2021. "**_Social Media Campaigns, Lobbying and Legislation: Evidence from #climatechange and Energy Lobbies._**"

- **Question**: To what extent do social media campaigns compete with fossil fuel lobbying on climate change legislation?

- Data include:
  - 5.0 million tweets with #climatechange/#globalwarming around the globe;
  - 12.0 million retweets/likes to those tweets;
  - 0.8 million Twitter users who wrote those tweets;
  - 1.4 million Twitter users who retweeted or liked those tweets;
  - 0.3 million US Twitter users with their location at a city level;
  - Firm-level lobbying data (expenses, targeted bills, etc.). 



## Instructor
### Economics and Data Science

- Choe, B.H. and Ore-Monago, T., 2024. "**_Governance and Climate Finance in the Developing World_**"

- **Climate finance** refers to the financial resources allocated for mitigating and adapting to climate change, including support for initiatives that reduce greenhouse gas emissions and enhance resilience to climate impacts.
  - We focus on *transnational financing* that rich countries provide poor countries with financial resources, in order to help them adapt to climate change and mitigate greenhouse gas (GHG) emissions.
  - Since the GHG emissions in developing countries are rapidly growing, it is crucial to assess the effectiveness of climate finance.
  - Poor governance (e.g., legal system, rule of law, and accountability) can be significant barriers to emissions reductions.


## Instructor
### Economics and Data Science

- Choe, B.H. and Newbold, Steve, "**_Estimating the Value of Statistical Life (VSL) through Big Data_**"

- VSL is the monetary value associated with reducing the risk of death. 
  - How much value would that be? How can we measure it?
  - How do government agencies use the VSL to decide which policies are worth the cost when they reduce the risk of death?




# Syllabus {background-color="#1c4982"}

## Syllabus

### Email, Class & Office Hours

- Email: [bchoe@geneseo.edu](bchoe@geneseo.edu)


- Class Homepage: 
  i. [GitHub Course Website](http://bcdanl.github.io){target="_blank"}
  i. [Brightspace Course Shell](https://mylearning.suny.edu/d2l/home/2232615){target="_blank"}
  
  
- Office: South Hall 227B
- Office Hours: 
  - Mondays and Wednesdays 3:30 P.M.--5:00 P.M.
  - By appointment via email.





## Syllabus

### Course Description

- This course is designed to provide a comprehensive overview of data handling techniques, focusing on practical application through case studies. 

- Key topics include: 
  1. data loading, cleaning, transformation, merging, and reshaping;
  2. techniques for slicing, dicing, and summarizing datasets;
  3. data collection via web scraping and APIs. 
  
- These areas will be explored through detailed, real-world examples to address common data analysis challenges. 

- Throughout the course, students will gain hands-on experience with **Python** and its data analysis libraries, along with practical applications of **git** and **GitHub**.



## Syllabus
### Reference Materials

- [**Python for Data Analysis** (3rd Edition)](https://wesmckinney.com/book){target="_blank"} by [Wes McKinney](https://wesmckinney.com/){target="_blank"}
  - A free online version of this book is available.

- [Python Programming for Data Science](https://www.tomasbeuzen.com/python-programming-for-data-science){target="_blank"} by Tomas Beuzen

- [Coding for Economists](https://aeturrell.github.io/coding-for-economists){target="_blank"} by Arthur Turrell 

- [Python for Econometrics in Economics](https://pyecon.org/lecture/}{https://pyecon.org/lecture/){target="_blank"} by Fabian H. C. Raters

- [QuantEcon DataScience - Python Fundamentals](https://datascience.quantecon.org/python_fundamentals/index.html){target="_blank"} by Chase Coleman, Spencer Lyon, and Jesse Perla

- [QuantEcon DataScience - pandas](https://datascience.quantecon.org/pandas/index.html){target="_blank"} by Chase Coleman, Spencer Lyon, and Jesse Perla

- [Guide for Quarto](https://quarto.org/docs/guide){target="_blank"}



## Syllabus
### Course Requirements


- **Laptop**: You should bring your own laptop (**Mac** or **Windows**) to the classroom. 
  - The minimum specification for your laptop in this course is 2+ core CPU, 4+ GB RAM, and 500+ GB disk storage.
  
- **Homework**: There will be six homework assignments.

- **Project**: There will be one project on a *personal website*.

- **Exams**: There will be two Midterm Exams and one Final Exam. 
  - The Midterm Exam 2 is comprehensive.
  - The Final Exam is comprehensive.

- **Discussions**: You are encouraged to participate in GitHub-based online discussions and class discussion, and office hours.
  - Checkout the netiquette policy in the syllabus.


## Syllabus
### Personal Website

- You will create your own website using Quarto, R Studio, and Git. 

- You will publish your homework assignments and a project on your website. 

- Your website will be hosted in [GitHub](https://www.github.com){target="_blank"}. 

- The basics in Markdown will be discussed.

- References:
  - [Quarto Guide](https://quarto.org/docs/guide){target="_blank"}


## Syllabus
### Why Personal Website?
:::{.nonincremental}
- Here is the example website:
  - [DANL Website Template](https://bcdanl.github.io/danl-website-template)

- **Professional Showcase**: Display skills and projects
- **Visibility and Networking**: Increase online presence
- **Content Sharing and Engagement**: Publish articles, insights
- **Job Opportunities**: Attract potential employers and clients
- **Long-term Asset**: A growing repository of your career journey

:::

## Syllabus
### Project

- The project report should include data collection and exploratory data analysis using summary statistics, visual representations, and data wrangling. 

- The document for the project must be published in each member's website. 




## Syllabus

### Class Schedule and Exams

- There will be tentatively 28 class sessions.

- The **Midterm Exam I** is scheduled on October 8, 2025, Wednesday, during the class time.

- The **Midterm Exam II** is scheduled on November 12, 2025, Wednesday, during the class time.

- The **Final Exam** is to be determined.


- The due for the **project** is December 16, 2025, Tuesday, 11:59 P.M., Eastern Time


## Syllabus

### Class Schedule and Exams

- No class on 
  - September 1 (*Labor Day*)
  - October 13 (*Fall Break*)
  - November 26 (*Thanksgiving Break*)





## Syllabus
### Course Contents

```{r, out.width='100%', fig.align='center'}
#| eval: true
#| echo: false
text_tbl <- data.frame(
  Week = c("1", "2-3", "4-7"),
  Contents = c("Course Outlines; Installing the Tools; Building a Website; Markdown",
"Python Basics with Google Colab",
"Filtering, Sorting, Ranking, Pivoting, Joining, and Concatenating DataFrames"),
  HW = c("", "1", "2")
  )


# Create a DT datatable without search box and 'Show entries' dropdown
DT::datatable(text_tbl, rownames = FALSE,
              options = list(
  dom = 't', # This sets the DOM layout without the search box ('f') and 'Show entries' dropdown ('l')
  paging = FALSE, # Disable pagination
  columnDefs = list(list(
    targets = "_all", # Applies to all columns
    orderable = FALSE # Disables sorting
  ))
), callback = htmlwidgets::JS("
  // Change header background and text color
  $('thead th').css('background-color', '#1c4982');
  $('thead th').css('color', 'white');

  // Loop through each row and alternate background color
  $('tbody tr').each(function(index) {
    if (index % 2 == 0) {
      $(this).css('background-color', '#d1dae6'); // Light color for even rows
    } else {
      $(this).css('background-color', '#9fb2cb'); // Dark color for odd rows
    }
  });

  // Set text color for all rows
  $('tbody tr').css('color', 'black');

  // Add hover effect
  $('tbody tr').hover(
    function() {
      $(this).css('background-color', '#607fa7'); // Color when mouse hovers over a row
    }, 
    function() {
      var index = $(this).index();
      if (index % 2 == 0) {
        $(this).css('background-color', '#d1dae6'); // Restore even row color
      } else {
        $(this).css('background-color', '#9fb2cb'); // Restore odd row color
      }
    }
  );
")
)

```

- The first part of the course covers Python basics and `pandas` basics.


## Syllabus
### Course Contents

```{r, out.width='100%', fig.align='center'}
#| eval: true
#| echo: false
text_tbl <- data.frame(
  Week = c("8-11", "12-13"),
  Contents = c(
"Web Scrapping with Selenium",
"Data Collection with Application Programming Interfaces (APIs)"
),
  HW = c("3", "4")
  )


# Create a DT datatable without search box and 'Show entries' dropdown
DT::datatable(text_tbl, rownames = FALSE,
              options = list(
  dom = 't', # This sets the DOM layout without the search box ('f') and 'Show entries' dropdown ('l')
  paging = FALSE, # Disable pagination
  columnDefs = list(list(
    targets = "_all", # Applies to all columns
    orderable = FALSE # Disables sorting
  ))
), callback = htmlwidgets::JS("
  // Change header background and text color
  $('thead th').css('background-color', '#1c4982');
  $('thead th').css('color', 'white');

  // Loop through each row and alternate background color
  $('tbody tr').each(function(index) {
    if (index % 2 == 0) {
      $(this).css('background-color', '#d1dae6'); // Light color for even rows
    } else {
      $(this).css('background-color', '#9fb2cb'); // Dark color for odd rows
    }
  });

  // Set text color for all rows
  $('tbody tr').css('color', 'black');

  // Add hover effect
  $('tbody tr').hover(
    function() {
      $(this).css('background-color', '#607fa7'); // Color when mouse hovers over a row
    }, 
    function() {
      var index = $(this).index();
      if (index % 2 == 0) {
        $(this).css('background-color', '#d1dae6'); // Restore even row color
      } else {
        $(this).css('background-color', '#9fb2cb'); // Restore odd row color
      }
    }
  );
")
)

```


- The second part of the course covers data collection.


## Syllabus
### Course Contents

```{r, out.width='100%', fig.align='center'}
#| eval: true
#| echo: false
text_tbl <- data.frame(
  Week = c("14-15"),
  Contents = c(
"Group Operations"
),
  HW = c( "5")
  )


# Create a DT datatable without search box and 'Show entries' dropdown
DT::datatable(text_tbl, rownames = FALSE,
              options = list(
  dom = 't', # This sets the DOM layout without the search box ('f') and 'Show entries' dropdown ('l')
  paging = FALSE, # Disable pagination
  columnDefs = list(list(
    targets = "_all", # Applies to all columns
    orderable = FALSE # Disables sorting
  ))
), callback = htmlwidgets::JS("
  // Change header background and text color
  $('thead th').css('background-color', '#1c4982');
  $('thead th').css('color', 'white');

  // Loop through each row and alternate background color
  $('tbody tr').each(function(index) {
    if (index % 2 == 0) {
      $(this).css('background-color', '#d1dae6'); // Light color for even rows
    } else {
      $(this).css('background-color', '#9fb2cb'); // Dark color for odd rows
    }
  });

  // Set text color for all rows
  $('tbody tr').css('color', 'black');

  // Add hover effect
  $('tbody tr').hover(
    function() {
      $(this).css('background-color', '#607fa7'); // Color when mouse hovers over a row
    }, 
    function() {
      var index = $(this).index();
      if (index % 2 == 0) {
        $(this).css('background-color', '#d1dae6'); // Restore even row color
      } else {
        $(this).css('background-color', '#9fb2cb'); // Restore odd row color
      }
    }
  );
")
)

```

- The third part of the course covers advanced `pandas`.


## Syllabus
### Grading

$$
\begin{align}
(\text{Total Percentage Grade}) =&\quad\;\, 0.05\times(\text{Attendance Score})\notag\\
&\,+\, 0.20\times(\text{Total Homework Score})\notag\\ 
&\,+\, 0.25\times(\text{Project and Website Score})\notag\\ 
&\,+\, 0.50\times(\text{Total Exam Score}).\notag
\end{align}
$$

## Syllabus
### Grading

- You are allowed up to 4 absences without penalty. 
  - Send me an email if you have standard excused reasons (illness, family emergency, transportation problems, etc.).

- For each absence beyond the initial five, there will be a deduction of 1% from the Total Percentage Grade.

- Participation will be evaluated by quantity and quality of GitHub-based online discussions and in-person discussion.

- The single lowest homework score will be dropped when calculating the total homework score.

  

## Syllabus
### Grading

$$
\begin{align}
&(\text{Midterm Exam Score}) \\
=\, &\text{max}\,\left\{0.50\times(\text{Midterm Exam I Score}) \,+\, 0.50\times(\text{Midterm Exam II Score})\right.,\notag\\ 
&\qquad\;\,\left.0.33\times(\text{Midterm Exam I Score}) \,+\, 0.67\times(\text{Midterm Exam II Score})\right\}.\notag
\end{align}
$$

- The Midterm Exam Score is the maximum between 
  1. the simple average of the Midterm Exam I score and the Midterm Exam II Score and
  2. the weighted average of them with one-third weight on the Midterm Exam I Score and two-third weight on the Midterm Exam II Score.
  
  
## Syllabus
### Grading

$$
\begin{align}
&(\text{Total Exam Score}) \\
=\, &\text{max}\,\left\{0.50\times(\text{Midterm Exam Score}) \,+\, 0.50\times(\text{Final Exam Score})\right.,\notag\\ 
&\qquad\;\,\left.0.25\times(\text{Midterm Exam Score}) \,+\, 0.75\times(\text{Final Exam Score})\right\}.\notag
\end{align}
$$


- The Total Exam Score is the maximum between 
  1. the simple average of the Midterm Exam Score and the Final Exam Score and
  2. the weighted average of them with one-fourth weight on the Midterm Exam Score and three-third weight on the Final Exam Score.


## Syllabus
### Make-up Policy

-  Make-up exams will not be given unless you have either a medically verified excuse or an absence excused by the University.

- If you cannot take exams because of religious obligations, notify me by email at least two weeks in advance so that an alternative exam time may be set.

- A missed exam without an excused absence earns a grade of zero.

- Late submissions for homework assignment will be accepted with a penalty. 

- A zero will be recorded for a missed assignment.




## Syllabus
### Academic Integrity and Plagiarism

-  All homework assignments and exams must be the original work by you. 

- Examples of academic dishonesty include:
  - *representing the work, thoughts, and ideas of another person as your own*
  - *allowing others to represent your work, thoughts, or ideas as theirs*, and
  - *being complicit in academic dishonesty by suspecting or knowing of it and not taking action*.


- Geneseo’s Library offers frequent workshops to help you understand how to **paraphrase**, **quote**, and **cite** outside sources properly. 
  - See [https://www.geneseo.edu/library/library-workshops](https://www.geneseo.edu/library/library-workshops){target="_blank"}.




## Syllabus
### Accessibility

-  The Office of Accessibility will coordinate reasonable accommodations for persons with physical, emotional, or cognitive disabilities to ensure equal access to academic programs, activities, and services at Geneseo.

- Please contact me and the Office of Accessibility Services for questions related to access and accommodations.





## Syllabus
### Well-being

- You are strongly encouraged to communicate your needs to faculty and staff and seek support if you are experiencing unmanageable stress or are having difficulties with daily functioning.

- Liz Felski, the School of Business Student Advocate ([felski@geneseo.edu](felski@geneseo.edu), South Hall 303), or the Dean of Students (585-245-5706) can assist and provide direction to appropriate campus resources.

- For more information, see [https://www.geneseo.edu/dean_students](https://www.geneseo.edu/dean_students){target="_blank"}.



## Syllabus
### Career Design

- To get information about career development, you can visit the Career Development Events Calendar ([https://www.geneseo.edu/career_development/events/calendar](https://www.geneseo.edu/career_development/events/calendar){target="_blank"}).

- You can stop by South 112 to get assistance in completing your Handshake Profile [https://app.joinhandshake.com/login](https://app.joinhandshake.com/login){target="_blank"}.
  - Handshake is ranked #1 by students as the best place to find full-time jobs.
  - 50% of the 2018-2020 graduates received a job or internship offer on Handshake.
  - Handshake is trusted by all 500 of the Fortune 500.


